---
title: "Intro"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
```{r,echo=FALSE,results='asis',warning=FALSE,message=FALSE}
source("app_server.R")
```
<h2>Analyzing Which Countries Have Reached Environmental Sustainability Using Greenhouse Gas Emission Per Capita and GDP Per Capita </h2>

<p>Greenhouse gas is gas in the atmosphere that traps heat and results in an increase in global temperature over time. It includes water vapor, carbon dioxide, methane, nitrous oxide, etc. The enormous amount of greenhouse gas increased in the atmosphere has been a critical factor resulting in many catastrophic atmospheric events. Therefore, regulating the emission of greenhouse gas has been one of the top priorities for countries worldwide. </p>
<p>Although countries should decrease greenhouse gas emissions as much as possible, other factors such as economic prosperity and the well-being of citizens are equally important to achieve environmental sustainability.  According to the three pillars of sustainability,  it is important for a country to find a balance between environmental viability, social equity, and environmental protection in environmental measures. Therefore, on this website, I used population(people), GDP (dollars), and greenhouse gas per capita (tons/capita)to analyze the performance of countries’ environmental measures. Because of the lack of data, we will only use GDP per capita, which is a great index to analyze the economic prosperity and the well-being of people in the country. Particularly, we can use this interactive visualization to find out which countries have found environmental sustainability, having low GHG per capita and high GDP per capita. </p>

<h2>Greenhouse Gas Emission Per Capita in 2019(Most Recent Year in Dataset)</h2>
<p>In 2019, the average greenhouse gas emissions across all countries is
```{r,echo=FALSE,results='asis',warning=FALSE}
print(values$average_2019)
print(123)
```
tons per capita. The highest emission is 
```{r,echo=FALSE,results='asis',warning=FALSE}
print(values$maxValue_2019)
```
tons per capita from 
```{r,echo=FALSE,results='asis',warning=FALSE}
print(values$maxC_2019)
```
.The lowest emission is 
```{r,echo=FALSE,results='asis',warning=FALSE}
print(values$minValue_2019)
```
tons per capita from 
```{r,echo=FALSE,results='asis',warning=FALSE}
print(values$minC_2019)
```
. The greenhouse emission has decreased by 
```{r,echo=FALSE,results='asis',warning=FALSE}
print(values$change_through_29_years)
``` 
tons per capita since 1990.<p>
